ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming

### 2012-03-13 papers/IJCSE/foropencl.tex
keywords
edits for final version

%% ANONYMIZED
%\LRH{M. Sottile et~al.}
\LRH{ }

@@

%% ANONYMIZED
\authorA{Author names removed for review}
% 1st. author
%\authorA{Matthew J. Sottile}
%\affA{Galois, Inc.\\
% Portland, OR 97204\\
% E-mail: mjsottile@computer.org}

% 2nd. author
%\authorB{Craig E Rasmussen}
%\affB{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: crasmussen@lanl.gov}

% 3rd. author
%\authorC{Wayne N. Weseloh}
%\affC{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: weseloh@lanl.gov}

% 4th. author
%\authorD{Robert W. Robey}
%\affD{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: brobey@lanl.gov}

% 5th. author
%\authorE{Daniel Quinlan}
%\affE{Lawrence Livermore National Laboratory\\
% Livermore, CA 94550\\
% E-Mail: dquinlan@llnl.gov}

% 6th. author
%\authorF{Jeffrey Overbey}
%\affF{National Center for Supercomputing Applications\\
% Champaign, IL 61820\\
% E-mail: overbey2@illinois.edu}

@@

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This work was supported in part by the Department of Energy Office of Science,
Advanced Scientific Computing Research.

@@

>>>>

%% ANONYMIZED
\LRH{M. Sottile et~al.}
%\LRH{ }

@@

%% ANONYMIZED
%\authorA{Author names removed for review}
% 1st. author
\authorA{Matthew J. Sottile}
\affA{Galois, Inc.\\
 Portland, OR 97204\\
 E-mail: mjsottile@computer.org}

% 2nd. author
\authorB{Craig E Rasmussen}
\affB{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: crasmussen@lanl.gov}

% 3rd. author
\authorC{Wayne N. Weseloh}
\affC{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: weseloh@lanl.gov}

% 4th. author
\authorD{Robert W. Robey}
\affD{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: brobey@lanl.gov}

% 5th. author
\authorE{Daniel Quinlan}
\affE{Lawrence Livermore National Laboratory\\
 Livermore, CA 94550\\
 E-Mail: dquinlan@llnl.gov}

% 6th. author
\authorF{Jeffrey Overbey}
\affF{National Center for Supercomputing Applications\\
 Urbana, IL 61801\\
 E-mail: overbey2@illinois.edu}

@@

\KEYWORD{Fortran; OpenCL; Accelerator programming; GPU programming; code generation.}

@@

%ACKNOWLEDGMENTS are optional

\section{Acknowledgments}
This work was supported in part by the Department of Energy Office of Science,
Advanced Scientific Computing Research.

@@

%% this was only required for review purposes - remove in final
%\newpage
%
%\input{note-to-reviewers}
